Differential Expression - HBCC - DLPFC - Dx

### 2020-08-24 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd
fix contrasts
scale vars to fix correlation

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```

@@

# Manually set comparison of SCZ-Other to Control
L = cbind(L1, L2, L3, data.frame(L4 = c(1, -0.5, -0.5, 0, 0, 0, 0, 0, 0)))

>>>>

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
adjust.covars <- glue::glue('scale({adjust.covars})')[-1]
formula <- glue::glue("~ 0 + Dx + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```

@@

# Manually set comparison of SCZ-Other to Control
L = cbind(L1, L2, L3, data.frame(L4 = c(1, -0.5, -0.5, 0, 0, 0, 0, 0)))
